---
title: "Assignment 3"
output: html_document
---


```{r setup}
knitr::opts_chunk$set(include  = TRUE)
library("httr")
library("xml2")
library("stringr")
library("rvest")
library(tidyverse)

```


```
https://pubmed.ncbi.nlm.nih.gov/?term=sars-cov-2+trial+vaccine+
```

Complete the lines of code:

```{r counter-pubmed, eval=TRUE}
# Downloading the website
website <- xml2::read_html("https://pubmed.ncbi.nlm.nih.gov/?term=sars-cov-2+trial+vaccine+")

# Finding the counts
counts <- xml2::xml_find_first(website, "/html/body/main/div[9]/div[2]/div[2]/div[1]/span")

# Turning it into text
counts <- as.character(counts)

# Extracting the data using regex
stringr::str_extract(counts, "[0-9,]+")
```
I was able to find 600 papers


```{r papers-covid-hawaii, eval=TRUE}
library(httr)
query_ids <- GET(
  url   = "https://eutils.ncbi.nlm.nih.gov/entrez/eutils/esearch.fcgi",
  query = list(db= 'pubmed',
               term = 'sars-cov2 trial vaccine',
               rettype = 'abstract',
                  retmax= 250)
)

# Extracting the content of the response of GET
ids <- httr::content(query_ids)
```
Why am I only getting 4 results from querying?


```{r get-ids, eval = TRUE}
# Turn the result into a character vector
ids <- as.character(ids)

# Find all the ids 
ids <- stringr::str_extract_all(ids, "<Id>[0-9,]+</Id>")[[1]]

# Remove all the leading and trailing <Id> </Id>. Make use of "|"
#ids <- stringr::str_remove_all(ids, "[^0-9]")
#ids <- stringr::str_remove_all(ids, "[</Id>]")
ids <- stringr::str_remove_all(ids, "<Id>|</Id>")
```

    
```{r get-abstracts, eval = TRUE}
ids2 <- ids
ids <- paste(ids, collapse=",")


publications <- GET(
  url   = "https://eutils.ncbi.nlm.nih.gov/entrez/eutils/efetch.fcgi",
  query = list(
    db = "pubmed",
    id = ids,
    retmax = 250,
    rettype = "abstract"
    )
)

# Turning the output into character vector
publications <- httr::content(publications)
publications_txt <- as.character(publications)
```


```{r one-string-per-response, eval = TRUE}
pub_char_list <- xml2::xml_children(publications)
pub_char_list <- sapply(pub_char_list, as.character)
```

```{r extracting-last-bit, eval = TRUE}
# pub_char_list

abstracts <- str_extract(pub_char_list, "<Abstract>(\\n|.)+</Abstract>")
abstracts <- str_remove_all(abstracts, "</?[[:alnum:]]+>")
abstracts <- str_replace_all(abstracts, "\\s+", " ")
table(is.na(abstracts))
```

```{r process-titles, eval = TRUE}
titles <- str_extract(pub_char_list, "<ArticleTitle>(\\n|.)+</ArticleTitle>")
titles <- str_remove_all(titles, "</?[[:alnum:]]+>")
titles <- str_replace_all(titles, "\\s+", " ")
titles
```

```{r}
journal <- str_extract(pub_char_list, "<Title>(\\n|.)+</Title>")
journal <- str_remove_all(journal, "</?[[:alnum:]]+>")
journal <- str_replace_all(journal, "\\s+", " ")
journal
```

```{r}
pubdate <- str_extract(pub_char_list, "<PubDate>(\\n|.)+</PubDate>")
pubdate <- str_remove_all(pubdate, "</?[[:alnum:]]+>")
pubdate <- str_replace_all(pubdate, "\\s+", " ")
pubdate

```


```{r build-db, eval = TRUE}
database <- data.frame(
  pubmed_id = ids2,
  title = titles,
  journal = journal,
  pubdate = pubdate,
  abstract = abstracts
)
knitr::kable(database)
```


############ Text Mining ############

```{r}
library(readr)
library(tidytext)
library(tidyverse)
pubmeds <- read_csv('https://raw.githubusercontent.com/USCbiostats/data-science-data/master/03_pubmed/pubmed.csv')

#count tokens in absracts
pubmeds %>%
  unnest_tokens(output=token, input = abstract) %>%
  count(token, sort=TRUE)

#stop words
pubmeds %>%
  unnest_tokens(word, input = abstract) %>%
  anti_join(stop_words) %>%
  filter(!(word %in% as.character(seq(0,100)))) %>%
  count(word, sort=TRUE) 

```

Before stop words, the counts include many articles. After, the main words include covid and other terms related to medical conditions, time states, and approaches. Covid, patients, cancer, prostate, and disease are the top 5 tokens.


```{r}

pubmeds %>%
  unnest_ngrams(word, input = abstract, n = 2) %>%
  anti_join(stop_words) %>%
  filter(!(word %in% as.character(seq(0,100)))) %>%
  count(word, sort=TRUE) %>%
  top_n(10, n) %>%
  ggplot(aes(x = n, y = fct_reorder(word,n))) + 
  geom_col()

```

###Question: How can I add stopwords to bigram visualization?


```{r}
pubmeds %>%
  unnest_tokens(token, abstract)%>%
  count(token, term) %>%
  bind_tf_idf(token, term, n) %>%
  arrange(desc(tf_idf))
```
The top five tokens are covid, prostate, eclampsia,  preeclampsia, and meningitis. These terms are more medically/condition specific than in quesiton 1. Before, there were generic terms like disease, cancer, and patient.